Results_setup

### 2020-04-21 src/Result_Setup.Rmd
changing the Rdata files across scripts

#outgroups
#SPIC
HetC.SPIC <- MLH1_data[(MLH1_data$strain == "SPIC")&(MLH1_data$quality < 5),]
#unique(HetC.SPIC$mouse)
#non-passing mice
SPIC.remove.mice <- c("30may18_SPIC_f1", "8jun18_SPIC_m2")
HetC.SPIC <- HetC.SPIC[ ! HetC.SPIC$mouse %in% SPIC.remove.mice, ]
#calq sex mean
SPIC.mean.MLH1.obs <- ddply(.data=HetC.SPIC, 
                 .(category),
                 summarize, 
                 ncells = length(unique(Original.Name)),
                 nmice = length(unique(mouse)),
                 mean.MLH1 = mean(adj_nMLH1.foci),
                 var.MLH1 = var(adj_nMLH1.foci)
)
SPIC.HETC.val <- SPIC.mean.MLH1.obs$mean.MLH1[1] / SPIC.mean.MLH1.obs$mean.MLH1[2]

#SPRET
HetC.SPRET <- MLH1_data[(MLH1_data$strain == "SPRET")&(MLH1_data$quality < 5),]
#unique(HetC.SPRET$mouse)
#non-passing mice
#SPRET.remove.mice <- c("", "")
#HetC.SPRET <- HetC.SPRET[ ! HetC.SPRET$mouse %in% SPRET.remove.mice, ]
#calq sex mean
SPRET.mean.MLH1.obs <- ddply(.data=HetC.SPRET, 
                 .(category),
                 summarize, 
                 ncells = length(unique(Original.Name)),
                 nmice = length(unique(mouse)),
                 mean.MLH1 = mean(adj_nMLH1.foci),
                 var.MLH1 = var(adj_nMLH1.foci)
)

@@

#CAROLI
HetC.CAROLI <- MLH1_data[(MLH1_data$strain == "CAROLI")&(MLH1_data$quality < 5),]
#unique(HetC.CAROLI$mouse)
#non-passing mice
#SPRET.remove.mice <- c("", "")
#HetC.SPRET <- HetC.SPRET[ ! HetC.SPRET$mouse %in% SPRET.remove.mice, ]
#calq sex mean
CAROLI.mean.MLH1.obs <- ddply(.data=HetC.CAROLI, 
                 .(category),
                 summarize, 
                 ncells = length(unique(Original.Name)),
                 nmice = length(unique(mouse)),
                 mean.MLH1 = mean(adj_nMLH1.foci),
                 var.MLH1 = var(adj_nMLH1.foci)
)

#cast
HetC.CAST <- MLH1_data[(MLH1_data$strain == "CAST")&(MLH1_data$quality < 5),]
#unique(HetC.CAST$mouse)
#non-passing mice
#X.remove.mice <- c("", "")
#HetC.SPRET <- HetC.SPRET[ ! HetC.SPRET$mouse %in% SPRET.remove.mice, ]
#calq sex mean
CAST.mean.MLH1.obs <- ddply(.data=HetC.CAST, 
                 .(category),
                 summarize, 
                 ncells = length(unique(Original.Name)),
                 nmice = length(unique(mouse)),
                 mean.MLH1 = mean(adj_nMLH1.foci),
                 var.MLH1 = var(adj_nMLH1.foci)
)
CAST.HETC.val <- CAST.mean.MLH1.obs$mean.MLH1[1] / CAST.mean.MLH1.obs$mean.MLH1[2]

#HMI
HetC.HMI <- MLH1_data[(MLH1_data$strain == "HMI")&(MLH1_data$quality < 5),]
#unique(HetC.HMI$mouse)
#non-passing mice
#X.remove.mice <- c("", "")
#HetC.SPRET <- HetC.SPRET[ ! HetC.SPRET$mouse %in% SPRET.remove.mice, ]
#calq sex mean
HMI.mean.MLH1.obs <- ddply(.data=HetC.HMI, 
                 .(category),
                 summarize, 
                 ncells = length(unique(Original.Name)),
                 nmice = length(unique(mouse)),
                 mean.MLH1 = mean(adj_nMLH1.foci),
                 var.MLH1 = var(adj_nMLH1.foci)
)

@@

```{r tot.skel.table, echo=FALSE}
totSC.mouse.av.table <- ddply(.data=MLH1.merge.Skel, 
                 .(mouse),
                 summarize, 
                 ncells = length(unique(Original.Name)),
                 nmice = length(unique(mouse)),
                # mean.MLH1 = mean(adj_nMLH1.foci, na.rm = TRUE),
                # var.MLH1 = var(adj_nMLH1.foci, na.rm = TRUE),

@@

```{r Save.File, echo=FALSE}
#save Rdata
save.image("~./MLH1repo/data/Results_setup_4.17.20.RData")
#save.image("data/BivData_4_PCA.RData")
```

>>>>

#outgroups
#SPIC
HetC.SPIC <- MLH1_data[(MLH1_data$strain == "SPIC")&(MLH1_data$quality < 5),]
#unique(HetC.SPIC$mouse)
#non-passing mice
SPIC.remove.mice <- c("30may18_SPIC_f1", "8jun18_SPIC_m2")
HetC.SPIC <- HetC.SPIC[ ! HetC.SPIC$mouse %in% SPIC.remove.mice, ]
#calq sex mean
SPIC.mean.MLH1.obs <- ddply(.data=HetC.SPIC, 
                 .(category),
                 summarize, 
                 ncells = length(unique(Original.Name)),
                 nmice = length(unique(mouse)),
                 mean.MLH1 = mean(nMLH1.foci),
                 var.MLH1 = var(nMLH1.foci)
)
SPIC.HETC.val <- SPIC.mean.MLH1.obs$mean.MLH1[1] / SPIC.mean.MLH1.obs$mean.MLH1[2]

#SPRET
HetC.SPRET <- MLH1_data[(MLH1_data$strain == "SPRET")&(MLH1_data$quality < 5),]
#unique(HetC.SPRET$mouse)
#non-passing mice
#SPRET.remove.mice <- c("", "")
#HetC.SPRET <- HetC.SPRET[ ! HetC.SPRET$mouse %in% SPRET.remove.mice, ]
#calq sex mean
SPRET.mean.MLH1.obs <- ddply(.data=HetC.SPRET, 
                 .(category),
                 summarize, 
                 ncells = length(unique(Original.Name)),
                 nmice = length(unique(mouse)),
                 mean.MLH1 = mean(nMLH1.foci),
                 var.MLH1 = var(nMLH1.foci)
)

@@

#CAROLI
HetC.CAROLI <- MLH1_data[(MLH1_data$strain == "CAROLI")&(MLH1_data$quality < 5),]
#unique(HetC.CAROLI$mouse)
#non-passing mice
#SPRET.remove.mice <- c("", "")
#HetC.SPRET <- HetC.SPRET[ ! HetC.SPRET$mouse %in% SPRET.remove.mice, ]
#calq sex mean
CAROLI.mean.MLH1.obs <- ddply(.data=HetC.CAROLI, 
                 .(category),
                 summarize, 
                 ncells = length(unique(Original.Name)),
                 nmice = length(unique(mouse)),
                 mean.MLH1 = mean(nMLH1.foci),
                 var.MLH1 = var(nMLH1.foci)
)

#cast
HetC.CAST <- MLH1_data[(MLH1_data$strain == "CAST")&(MLH1_data$quality < 5),]
#unique(HetC.CAST$mouse)
#non-passing mice
#X.remove.mice <- c("", "")
#HetC.SPRET <- HetC.SPRET[ ! HetC.SPRET$mouse %in% SPRET.remove.mice, ]
#calq sex mean
CAST.mean.MLH1.obs <- ddply(.data=HetC.CAST, 
                 .(category),
                 summarize, 
                 ncells = length(unique(Original.Name)),
                 nmice = length(unique(mouse)),
                 mean.MLH1 = mean(nMLH1.foci),
                 var.MLH1 = var(nMLH1.foci)
)
CAST.HETC.val <- CAST.mean.MLH1.obs$mean.MLH1[1] / CAST.mean.MLH1.obs$mean.MLH1[2]

#HMI
HetC.HMI <- MLH1_data[(MLH1_data$strain == "HMI")&(MLH1_data$quality < 5),]
#unique(HetC.HMI$mouse)
#non-passing mice
#X.remove.mice <- c("", "")
#HetC.SPRET <- HetC.SPRET[ ! HetC.SPRET$mouse %in% SPRET.remove.mice, ]
#calq sex mean
HMI.mean.MLH1.obs <- ddply(.data=HetC.HMI, 
                 .(category),
                 summarize, 
                 ncells = length(unique(Original.Name)),
                 nmice = length(unique(mouse)),
                 mean.MLH1 = mean( nMLH1.foci),
                 var.MLH1 = var( nMLH1.foci)
)

@@

```{r tot.skel.table, echo=FALSE}
totSC.mouse.av.table <- ddply(.data=MLH1.merge.Skel, 
                 .(mouse),
                 summarize, 
                 ncells = length(unique(Original.Name)),
                 nmice = length(unique(mouse)),
                # mean.MLH1 = mean( nMLH1.foci, na.rm = TRUE),
                # var.MLH1 = var( nMLH1.foci, na.rm = TRUE),

@@

```{r Save.File, echo=FALSE}
#save Rdata
save.image("~./MLH1repo/data/Results_setup_4.21.20.RData")
#save.image("data/BivData_4_PCA.RData")
```
